Practical Effects of Integrating Temperature with Strang Split Reactions

### 2021-03-12 strang/paper.tex
Clarify referent of this
remove redundant text

\item Evolve $(X_k, T)$.   This is used in \cite{Pakmor:2012} and
  \cite{Garcia-Senz:2013}.  To avoid expensive equation of state calls
  in getting the specific heat, we can optionally ``freeze'' the value
  of $c_v$ at the start of integration to avoid potentially expensive
  equation of state calls.  This was discussed in \cite{Bell:2004} and
  until recently was the default method in \castro.

@@

Looking at global convergence of a reacting hydrodynamics problem we
see that second order convergence is only realized when temperature or
energy is evolved alongside the composition when using a Strang-split
approach to reactions.  This is just a single, rather simple problem,
but this suggests that reactive hydrodynamics simulations should
switch to integrating temperature or another energy equation together
with reactions to yield better overall convergence and accuracy.  This
complements the work of \citep{muller:1986} which showed that when
evolving near nuclear statistical equilibrium, that evolving entropy
with the system is needed for stability.  We expect that for problems
with vigorous burning, such as detonations, this will be especially
important.

>>>>

\item Evolve $(X_k, T)$.   This is used in \cite{Pakmor:2012} and
  \cite{Garcia-Senz:2013}.  To avoid expensive equation of state calls
  in getting the specific heat, we can optionally ``freeze'' the value
  of $c_v$ at the start of integration.  This was discussed in \cite{Bell:2004} and
  until recently was the default method in \castro.

@@

Looking at global convergence of a reacting hydrodynamics problem we
see that second order convergence is only realized when temperature or
energy is evolved alongside the composition when using a Strang-split
approach to reactions.  This is just a single, rather simple problem,
but this suggests that reactive hydrodynamics simulations should
switch to integrating temperature or another energy equation together
with reactions to yield better overall convergence and accuracy.  This
complements the work of \citep{muller:1986} which showed that when
evolving near nuclear statistical equilibrium, that evolving entropy
with the system is needed for stability.  We expect that for problems
with vigorous burning, such as detonations, directly coupling the composition
and thermodynamic evolution will be especially important.
